Draft

### 2017-08-26 Thesis/Draft.Rmd
Rewritten Setup

# Thresholding Bandit Problem

The *Thresholding Bandit Problem* described in Locatelli et al. (2016) can be considered a variant of a variant. It can be framed inside of the wider literature of *Pure Exploration* multi-armed bandit problems. In particular, it shares characteristics with the *Top-$m$* problem. This problem is concerned with finding the $m$ best arms as described by the means of their corresponding distributions. This in turn is similar to the *combinatorial bandit* problem, which also aims at finding the $m$ best arms. However, it is able to pull several arms at once: Think of an online shop that shows five recommended products on a product detail page. These five recommended products might each be represented by an arm, and we look for the products with the largest mean conversion rate. The thresholding bandit problem we discuss here, however, is concerned with pulling a single arm at a time. And so a more appropriate situation is that of a website presenting a banner. Again, think of an online shop trying to promote a certain category. The content team came up with a number of different designs for the banner, and it's not clear how many click-throughs they will gather.

The idea now is that we would like to classify the banners into two distinct groups: A group with mean conversion rates $\mu_i$ below threshold $\tau$, and a group with mean conversion rates $\mu_i$ above threshold $\tau$. This might be the optimization problem when we are concerned with not falling below a certain minimum level click-through rate with the banners we're choosing.

If it turns out that in general we can find relatively quickly whether arms are above or below a threshold, then this kind of test can be used to safeguard against very bad versions in a test. Before we move to a Top-$m$ test, we might want to run a thresholding version and then continue only with the arms classified into the group above the threshold. This might be justified when adjusting parts of the checkout process of an online shop, where the conversion rate or the average order value should not drop below a threshold.

@@

@@

**Remark**: Obviously, the APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$. This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most. That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold. In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$. Consequently, other arms farther away from the threshold will be sampled again. In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.

>>>>

# Thresholding Bandit Problem \label{Chapter_TBM}

To introduce the thresholding bandit problem, consider a game in which the learner is tasked to find those slot machines within a row of $K$ slot machines in a casino that give a mean payoff larger than a fixed threshold $\tau$, for example $\tau = 0$. The learner cannot pull all slot machines at the same time. Instead, he acquires samples sequentially from one slot machine at a time to learn about their payoff structure. The learner has a budget of $T$ slot machine pulls. After $t-1$ samples, the learner has observed $T_i(t-1)$ samples from slot machine $i$. The payoffs $X_{i,1}, ..., X_{i,T_i(t-1)}$ are drawn from the payoff distribution $\nu_i$ underlying the slot machine $i$. At time $t$, the learner considers the payoffs he observed so far in order to choose the next slot machine he would like to pull. His decision is lead by the goal to classify the slot machines with distribution $\nu_i$ and mean payoff $\mu_i$ after $T$ samples as being above or below the threshold with error probability as small as possible.

The thresholding bandit problem can thus be framed in the wide literature on sequential sampling strategies. While its name is reminiscient of the multi-armed bandit setting, the thresholding bandit problem is more akin to best arm identification and Top-$m$ identification problems due to its focus on exploration: While the classical multi-armed bandit problems are concerned with cumulative regret which increases *during* sampling, best arm identification and thresholding bandits collect loss only once *after* the sampling procedure (compare Garivier and Kaufmann, 2016; Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013). Furthermore, as there arises an implicit threshold between the means of the $m$-th best arm and the $m+1$-th best arm (Kaufmann et al., 2016; Kaufmann and Kalyanakrishnan, 2013), algorithms for the Top-$m$ identification problem classify arms at least implicitly as being above or below a threshold. The two settings are thus very related.

@@

Consider a setting of $i=1, ..., K$ unknown probability distributions $\nu_i$. To stick with the idea of multi-armed bandits, we call those distributions arms, and observations from those arms rewards (Bubeck and Cesa-Bianchi, 2012). The learner is interested in learning about the structure of the arms; in particular, he would like to estimate the means $\mu_1, ..., \mu_K$ by sequentially drawing observations $X_{i,1}, X_{i,2}, ...$ from each arm. However, at time $t$ the learner cannot observe a reward from every distribution but must select a single arm $I_t$ from which he would like to observe the reward $X_{I_t,t}$. An adaptive sampling strategy makes the decision of which arm to pull usually by computing an index $B_i(t)$ for each arm. If $T_i(t)$ is the number of samples observed until time $t$ for arm $i$, then $B_i(t)$ is a function of the past rewards $X_{i,1}, ..., X_{i,T_i(t)}$ observed for arm $i$, and w.l.o.g. $I_t = \arg \min_{i = 1,...K} B_i(t)$. The set of indices can be called strategy (Kaufmann et al., 2012) which makes it clear that the strategy is adapted as more observations are collected. Strategies of this kind are also called index policies.

What index proves to be useful is determined by the loss function with which the decisions of the algorithm are evaluated. While many problems are concerned with finding the arm with the largest mean $\mu_i$, in which algorithms collect loss either cumulatively (Auer and Cesa-Bianchi, 2012) or once at the end of the sampling (Kaufmann et al., 2016), the thresholding bandit problem considers a slightly different loss function. Consider a fixed threshold value $\tau \in \mathbb{R}$ and an epsilon interval $\tau \pm \epsilon$ around the threshold for $\epsilon \geq 0$.

------------ Old

@@

The APT algorithm tends to pull arms more often with corresponding mean close to the threshold and interval (small $\hat{\Delta}_i(t))$. This makes sure that more evidence is gathered on arms which appear to be inherently difficult to classify based on the samples collected until time $T_i(t)$, as these arms stifle the confidence the most. That is, until we have collected enough evidence to make a confident classification even if the mean is truly close to the threshold. In that case, $\sqrt{T_i(t)}$ will raise $B_i(t+1)$. Consequently, other arms farther away from the threshold will be sampled again. In this way, the algorithm tries to distribute the budget $T$ over all arms so as to define a sampling rule optimizing the confidence of the final decision.

Locatelli et al. (2016) show that the APT algorithm is optimal in the sense that the upper bound on its expected loss reaches the lower bound for the expected loss.
